A Novel Sampling Method Using Stochastic Gradient Descent

### 2016-12-07 paper/main.tex

\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\caption{$d(k)$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). It can be seen that $d(k)$ decreases exponentially for all of the functions. And the mixing time decreases as the degree increases.}\label{Fig:sim3_1}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\caption{Empirical density of $x^k$ for $k = 100$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). For $\exp(-|x|)$, it has not converge to the true pdf yet. For $\exp(-|x|^4)$, it has already converged.}\label{Fig:sim3_2}
\end{figure}
As shown in Figure \ref{Fig:sim3_1} and Figure \ref{Fig:sim3_2}, the mixing time of $\exp(-|x|)$ is the longest ($>$ 100) and the mixing time of $\exp(-|x|^4)$ is the shortest. This is coherent with their convergence time. For $\exp(-|x|)$, the convergence time is the longest; for $\exp(-|x|^4)$, the convergence time is the longest.

@@

% section discussion (end)
% \newpage
% ===================================================================================
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
% \appendix

% \section{Section in Appendix}
% \label{appendix-sec1}

% Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
% Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
% Sample text.

>>>>

\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case2_l1.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case3_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case4_l1.pdf}
\caption{$d(k)$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). It can be seen that $d(k)$ decreases exponentially for all of the functions. And the mixing time decreases as the degree increases.}\label{Fig:sim3_1}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case2_pdf.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case3_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case4_pdf.pdf}
\caption{Empirical density of $x^k$ for $k = 200$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). For $\exp(-|x|)$, it has not converge to the true pdf yet. For $\exp(-|x|^4)$, it has already converged.}\label{Fig:sim3_2}
\end{figure}
As shown in Figure \ref{Fig:sim3_1} and Figure \ref{Fig:sim3_2}, the mixing time of $\exp(-|x|)$ is the longest ($>$ 100) and the mixing time of $\exp(-|x|^4)$ is the shortest. This is coherent with their convergence time. For $\exp(-|x|)$, the convergence time is the longest; for $\exp(-|x|^4)$, the convergence time is the longest.

@@

% section discussion (end)
% \newpage
% ===================================================================================
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix
\tiny
\lstinputlisting[language=python]{../code/final/1_1/convergence.py}
\lstinputlisting[language=python]{../code/final/1_1/example1_1.ipy}
\lstinputlisting[language=python]{../code/final/1_1/simulation.py}
\lstinputlisting[language=python]{../code/final/1_1/mixing.py}
\lstinputlisting[language=python]{../code/final/1_1/proof_of_concept.py}
